Figures to insert in text

### 2018-04-09 Chapters/Chapter01.tex
details here and there

\begin{flushright}{\slshape
    {We are watching History being made --- or History being repeated.}
	\\ \medskip
    --- David Collum, Cornell University, 2013}
\end{flushright}
\bigskip
\bigskip

The main problem when one is trying to create digital money is how to prevent double spending. As the money is digital, and copies can be made \textit{ad nauseam}, what can prevent counterfeiting? That is, what would prevent users from sending copies of the same money to two (or more) people? That is precisely the problem solved by Bitcoin and its underlying blockchain technology. The current solution behind fiat money is having a single issuer, a central bank, and trusting the financial institutions.

>>>>

\begin{flushright}{\slshape
    {Once I understood the logic behind change addresses...\\
    $ripemd160( SHA256( pubkey ) )$... the inneficiency... \\
    the wasted space; the wasted energy... something clicked.\\
    \medskip

    This is military-grade cryptography and full-blown paranoia.\\
    Whoever did it hears voices whispering `they know everything.' \\
    \medskip

    Other than that, it's a get-rich-quick-scheme \\
    that looks exactly like a get-rich-quick-scheme.}
	\\ \medskip
    --- Alex Linhares, EBAPE/FGV

        \bigskip
        \bigskip
        \bigskip
        \bigskip

    {We are watching History being made.\\
    Or History being repeated.}
	\\ \medskip
    --- David Collum, Cornell University, 2013}
\end{flushright}
\bigskip
\bigskip
\bigskip
\bigskip

The main problem with digital money is how to prevent double spending. As the money is digital, and copies can be made \textit{ad nauseam}, what can prevent counterfeiting? That is, what would prevent users from sending copies of the same money to two (or more) people? That is precisely the problem solved by Bitcoin and its underlying blockchain technology. The current solution behind fiat money is having a single issuer, a central bank --- then trusting the financial institutions.

### 2018-04-09 Chapters/Chapter02.tex
details here and there

    \item Learning Intelligent Distribution Agent (LIDA) developed by Stan Franklin's lab at the University of Memphis includes implementation of SDM in Java: http://ccrg.cs.memphis.edu/framework.html;

@@

Let us analyse these.  The Connection Machine is obsolete.  The NASA implementation is hardware-based, hence not open-source.  APL, while influential, is not a mainstream language in science.

@@

Then there is LIDA --- a whole cognitive architecture based on Hofstadter's Fluid Concepts, Kanerva's SDM, and other ideas.  It is developed in Java; which makes it difficult to connect to the lowest levels of hardware; to connect to GPUs or FPGAs, and to other languages --- at least in comparison to Python\footnote{Python is sometimes called a `glue language'. That is, in my opinion, not the best metaphor.  A glue connects two things leaving an inflexible structure.  Python is perhaps best described as the interstate highway system of Programming; if something is out there, there is a way to reach it with Python.  In the comparison with Java, for instance, take the $popcnt(xor(b_i,b_j))$ operation, executed billions of times in SDM. How easy is it to program that for a particular GPU or FPGA with Java?}.  It is not available on an open-source repository.  It has a non-standard license, strange to the open-source community, ``the LIDA Framework Software NonExclusive, Non-Commercial Use License''.  Potential contributors must sign an ``Agreement Regarding Contributory Code for the LIDA Framework Software''... \emph{`before Memphis can accept it'}.

@@

    \item The whole SDM code is composed of 143 \emph{lines} of C++ in the $cstk/cstk-devonly/sdm$ folder.
0
    \item There is no work on making the system parallel.

@@

    \item There are no publishable / published scientific applications or experiments available to be reproduced.

@@

Another issue is \emph{extensibility}: Extensions of SDM have been used in many applications. For example, \citet{Snaider2011} extended SDM to store sequences of vectors and trees efficiently.  \citet{Rajesh1998} used a modified SDM in an autonomous robot. \citet{Meng2009} modified SDM to clean patterns from noisy inputs. \citet{fan1997genetic} extended SDM with genetic algorithms. \citet{chada2016you} extended SDM creating the Rotational Sparse Distributed Memory (RSDM), which is used to modeling network motifs, dynamic flexibility, and hierarchical organization, all results from neuroscience literature.

@@

This time, however, it will be running on a computer.

>>>>

    \item Learning Intelligent Distribution Agent (LIDA) developed by Stan Franklin's lab at the University of Memphis includes implementation of SDM in Java. \footnote{http://ccrg.cs.memphis.edu/framework.html};

@@

Let us analyse these.  The Connection Machine is obsolete.  The NASA implementation is hardware-based and obsolete.  APL, while influential, is not a mainstream language in science.

@@

Then there is LIDA --- a whole cognitive architecture based on Hofstadter's Fluid Concepts, Kanerva's SDM, and other ideas \citep{Anwar2003, snaider_integer_2013, snaider_modular_2014, franklin_lida:_2014}.  It is developed in Java; which makes it difficult to connect to the lowest levels of hardware; to connect to GPUs or FPGAs, and to other languages --- at least in comparison to Python\footnote{Python is sometimes called a `glue language'. That is, in my opinion, not the best metaphor.  A glue connects two things leaving an inflexible structure.  Python is perhaps best described as the interstate highway system of Programming; if something is out there, there is a way to reach it with Python.  In the comparison with Java, for instance, take the $popcnt(xor(b_i,b_j))$ operation, executed billions of times in SDM. How easy is it to program that for a particular GPU or FPGA with Java?}.  It is not available on an open-source repository.  It has a non-standard license, strange to the open-source community, \emph{the LIDA Framework Software NonExclusive, Non-Commercial Use License}.  Moreover, potential contributors must sign an ``Agreement Regarding Contributory Code for the LIDA Framework Software''... \emph{`before Memphis can accept it'} \footnote{What they are attempting to do with this bureaucracy remains unknown, the history of computing has not been kind to those who favored centralization \citep{ferguson_computer_2002}.}.

@@

    \item The whole SDM code is composed of 143 \emph{lines} of C++ in the $cstk/cstk-devonly/sdm$ folder.

    \item There is no work on making the system parallel.

@@

    \item There are no publishable or published scientific applications or experiments available to be reproduced at installation time.

@@

Another issue is \emph{extensibility}: Extensions of SDM have been used in many applications. For example, \citet{Snaider2011} extended SDM to store sequences of vectors and trees efficiently.  \citet{Rajesh1998} used a modified SDM in an autonomous robot. \citet{Meng2009} modified SDM to clean patterns from noisy inputs. \citet{fan1997genetic} extended SDM with genetic algorithms. \citet{chada2016you} extended SDM creating the Rotational Sparse Distributed Memory (RSDM), which models network motifs, dynamic flexibility, and hierarchical organization --- reflecting results from the neuroscience literature.

@@

This time, however, it will be running on a computer:  implicit assumptions will emerge; anomalies between expected theory and numerical results will appear; and reproducible experiments will be conducted.

### 2018-04-09 Chapters/Chapter0A.tex
details here and there

Finally, how long does it take for a dissertation to be completed? The time is either less than or equal to the duration allowed by the Grad College for the completion of a Ph.D or it is greater. In the latter case, infinite number of petitions can be filed for extensions. Since the Grad College never remembers previous petitions, the total number of petitions received by the Grad College is always one, a small constant\footnote{Bala Rajagopalan, Internet usenet rec.humor.funny, June 12 1989, `with apologies to non-cs types'.}. (QED)

>>>>

Finally, how long does it take for a dissertation to be completed? The time is either less than or equal to the duration allowed by the Grad College for the completion of a Ph.D or it is greater. In the latter case, infinite number of petitions can be filed for extensions. Since the Grad College never remembers previous petitions, the total number of petitions received by the Grad College is always one, a small constant\footnote{`With apologies to non-CS types': this wonderful result is from Bala Rajagopalan, posted on the late rec.humor.funny Usenet in June 12 1989.}.

\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip

\hfill \emph{Quod Erat Demonstrandum}

### 2018-04-09 Chapters/sdm-autocorrelation.tex
details here and there

The bias begins in the counters. Let's analyze the $i$th counter of a hard location.

@@

Let $Y_i$ be the number of bitmatches in the $i$bit of a hard location's address after $s$ written bitstrings. Then, $Y_i = \sum_{k=1}^{\theta} X_k$.

\begin{theorem}
Giving the number of written bitstrings $s$, $\mathbf{E}[Y_i] = \mu_Y = p \mu_\theta$ and $\mathbf{V}[Y_i] = \sigma^2_Y = p(1-p) \mu_\theta + p^2 \sigma^2_\theta$.
\end{theorem}
\begin{proof}
Applying the law of total expectation, $\mathbf{E}[Y] = \mathbf{E}[\mathbf{E}[Y|\theta]] = \mathbf{E}[p \theta] = p \mathbf{E}[\theta] = p \mu_\theta$.

>>>>

The previous theorems show that there is bias in the counters. Let us analyze the $i$th counter of a hard location.

@@

Let $Y_i$ be the number of bitmatches in the $i$ of a hard location's address after $s$ written bitstrings. Then, $Y_i = \sum_{k=1}^{\theta} X_k$.

\begin{theorem}
Given the number of written bitstrings $s$, $\mathbf{E}[Y_i] = \mu_Y = p \mu_\theta$ and $\mathbf{V}[Y_i] = \sigma^2_Y = p(1-p) \mu_\theta + p^2 \sigma^2_\theta$.
\end{theorem}
\begin{proof}
Applying the law of total expectation, $\mathbf{E}[Y] = \mathbf{E}[\mathbf{E}[Y|\theta]] = \mathbf{E}[p \theta] = p \mathbf{E}[\theta] = p \mu_\theta$.
